%-----------------------------------------------------------------------------
%
%	formulat.tex Document formulation part
%
%	INCLUDE FILE FOR LaTeX2e DOCUMENT
%
%	AUTHOR: Ari Potkonen /JARVENPAA/ Mon Dec 11 2023
%-----------------------------------------------------------------------------
%        1         2         3         4         5         6         7
%23456789012345678901234567890123456789012345678901234567890123456789012345678
%-BEGIN OF INCLUDE FILE-------------------------------------------------------
\begin{comment}\end{comment}
\chapter{Mathematical formulation}

The most needed gap fillings for Nuclides chart\allowbreak\cite{Nuclides} are
now done, and it's time to be able to understand fully local space of electron
and positron. How space is curled and how electromagnetic $\gamma$ -ray lives
there according the Maxwell's equations in curved spacetime\allowbreak\cite{
MaxwellsEquations}, or now with the new formation for relative non-linear
causality supporting space without time. Dynamic process of electron-positron
annihilation\allowbreak\cite{Annihilation} opening the curls and releasing of
$\gamma$ -rays. Pair production\allowbreak\cite{PairProduction} starting from
"triplet production". Continuing with the proton, antiproton, neutron,
antineutron static representations without and with superpositioned electrons
or pos\-i\-trons. Then proceeding what happens on other collected Feynmann
diagrams\allowbreak\cite{FeynmannDiagram}. You are welcomed to continue this
work and fill the missing.

\section{Static electron and static positron}
\label{electron_positron}
\index{electron}
\index{positron}

There is need to understand electron and positron local space curling,
electric field in curled space and how this looks from remote static
observer viewpoint\allowbreak\cite{ElectronVideo}. All in detail.

Most obvious answer is to have Maxwell equations for curved spacetime, but
now with causality support, without spacetime and large scale gravitation
affects in it, and with the Schwinger limit\allowbreak\cite{SchwingerLimit}
related nonlinearity terms based to field strength included into. Terms which
then give expected solution for the electron, seen in the referred
video\allowbreak\cite{ElectronVideo} at femto-attometer scale in form of
resting curled wave caused quantized space curvature having gravity effect.
Large scale integrations should brings equations equivalent to currently
known Maxwell equations in curved space.

\section{Annihilation}
\label{annihilation}
\index{annihilation}

Original curls in detail, how waves summing at cross section of curls and how
this leads to curl opening and $\gamma$ -rays release. Curved non-linear
space "Gravity" behaviour during curl curvature opening, localized energy
dwell's non-linear space straightening -- linearization.

\section{Pair production}
\label{pair_production}
\index{pair production}

Incoming $\gamma$ -ray wavelets. Curl creation in electron collision. Curl
own local non-linear space curvature development and from outside observers
point static situation after that. Formulation of discrete curl curvature
form, and it's relation to gravity.

\begin{comment}\end{comment}
%-END OF INCLUDE FILE---------------------------------------------------------
