%-------------------------------------------------------------------------------
%
%	story.tex Document supposition part
%
%	INCLUDE FILE FOR LaTeX2e DOCUMENT
%
%	AUTHOR: Ari Potkonen /JARVENPAA/ Mon Dec 11 2023
%------------------------------------------------------------------------------
%         1         2         3         4         5         6         7
%123456789012345678901234567890123456789012345678901234567890123456789012345678
%-BEGIN OF INCLUDE FILE--------------------------------------------------------
\begin{comment}\end{comment}
\chapter{Guessing correct answer}
\section{Supposition}
\label{supposition}
\index{supposition}
Our generally relativistic world we see consists only from electromagnetism,
energy and space. Nothing else is there !

Electromagnetism itself is kind of progressing phenomenon, supporting causality
and offers for humans possibility to define time, which is handy for modeling
and tracking this causality, but time definition itself is based to
electromagnetism, energy and space, the major ingredients what just proposed
for our generally relativistic world.

\section{Hypothesis}
\label{hypothesis}
\index{hypothesis}

Hypothesis is that subatomic particles electron, positron, proton and
antiproton are actually pure electromagnetic waveforms curled up in it's own
space.

Schwinger limit (Julian Schwinger \cite{SchwingerLimit}) gives limits for
electric field $E_c~=1.23 EV/m$ (Eksa Volt / meter) and magnetic field
$B_c~=4.41 GT$ (Giga Tesla) after we can see nonlinearity in scale of
electron Compton wavelength (Arthur Compton \cite{ComptonWavelength}) 
$\lambda_e=2426 fm$.


Strong electromagnetic fields in Compton wavelength scale
$(\lambda=\frac{h}{mc})$
can produce discrete numerable curled waveforms
$(\bar{\lambda}=\frac{\lambda}{2\pi})$,
$\bar{\lambda}_e=386 fm$,
%\bar{\lambda}\lambdabar\lambdaslash\textcrlambda
harmonics where wave goes with light speed, but from local observers
perspective outside from curled space, human defined time seems to be stopped
and we see kind of frozen representation from curled wave.

\begin{equation} \label{eq:reduced_plank_constant} 
	\hbar
	= \frac{6.582119569}{10^{16}}[eVs]
	= \frac{1.054571817}{10^{34}}[Js]
\end{equation}

\begin{equation} \label{eq:plank_constant} % SI-units and other 
	h
	= \frac{4.135667696}{10^{15}}\left[\frac{eV}{Hz}\right]
%	= \frac{1.602176634C\cdot4.135667696V}{10^{34}Hz}
%	= \frac{1.602C\cdot4.136V}{10^{34}Hz}
	= \frac{6.62607015}{10^{34}}\left[\frac{J}{Hz}\right]
\end{equation}

\begin{equation} \label{eq:electron_rest_mass}
	m_e=\frac{E_e}{c^2}
%	=\frac{E_e [eV]}{c^2 \left[\frac{m^2}{s^2}\right]}
%	=m_e\frac{[J]}{\left[\frac{m^2}{s^2}\right]}
%	=m_e\frac{[kg\frac{m^2}{s^2}]}{\left[\frac{m^2}{s^2}\right]}
%	=m_e[kg]
\end{equation}

Electron curled spacetime radius $\bar{\lambda}_e$ is
\begin{equation} \label{eq:gamma_lenght} % Electron annihilation induced gamma ray wavelength 
	\bar{\lambda}_e=\frac{\hbar}{m_ec}
	=\frac{\hbar c}{E_e}
	=\frac{6.58eVs\cdot299\frac{m}{s}}{10^{13}\cdot511eV}
%	=\frac{6.582119569eVs\cdot299792458\frac{m}{s}}{10^{16}\cdot510998.95069eV}
	=386fm
%	=386.159267407fm
%	=0.386pm
\end{equation}
and diameter $\diameter_e=772 fm$.


Electron annihilation released $\gamma$ -photon wavelenght $\lambda_\gamma$ is
\begin{equation} \label{eq:gamma_lenght} % Electron annihilation induced gamma ray wavelength 
	\lambda_\gamma=\frac{h}{m_ec}
%	=\lambda_\gamma\frac{\left[\frac{eV}{Hz}\right]}{[kg]\left[\frac{m}{s}\right]}
%	=\lambda_\gamma\frac{[Js]}{\left[kg\frac{m}{s}\right]}
%	=\lambda_\gamma\frac{\left[kg\frac{m^2}{s}\right]}{\left[kg\frac{m}{s}\right]}
%	=\lambda_\gamma[m]
	=\frac{hc}{E_e}
	=\frac{4.14eVs\cdot299\frac{m}{s}}{10^{12}\cdot511eV}
%	=\frac{4.135667696eVs\cdot299792458\frac{m}{s}}{10^{15}\cdot510998.95069eV}
%	=2436 fm
	=2.436pm
%	=2.42631023867(73)pm % https://physics.nist.gov/cgi-bin/cuu/Value?ecomwl
\end{equation}

There are few possibilities what has happened so that electron, positron could
hold that electromagnetic wavelet -- $\gamma$ photon electromagnetic energy in
after pair profuction; Either space is bending with light speed in curl so wave
seems to be static or time, as we understand it, has been stopped because wave
in curl curving proceeds with light speed or both because light speed is
reached in formed curl. It's kind of total internal reflection forming standing
wave having only one peak visible for externals and other peak is fully
internal, only visible inside of curl. This bending makes curled wave behave
like noticeable charged particle, still being a discrete standing wave due to
unlinearity making it possible to exist.

Curling can create discrete numbered relativistic bending forms to space, and
we call known stable curl forms to electron, positron, proton and antiproton.

Each curl's bend space around and bending is called to gravity. Known lowest
energy curls are electron and positron. Electron curl outside visible electric
field is negative and other handed antiparticle positron has positive electric
towards outside.

Because of this outside bended electric field, local observer can accelerate
and move electrons and positrons using external electromagnetic field. When
electron, it's curl is accelerated with the external electric field it will
face relativistic Doppler effect it's wave is coming shorter which means that
curled wave gains more energy and more mass. While decelerated curl wavelength
widens and energy is lost to breaking against the external field.

Proton and antiproton next energy rich left and right hand sided
electromagnetic field stable curls we know. Proton has positive field outwards
and antiproton has negative field outwards. While energy is much bigger than
electron has the wavelength of curl is shorter and curl size is smaller. Tight
curl forms stronger bend to space and we see it as stronger gravity.

Electron negative electric field and proton positive electric field pull curls
towards each other and those can superposition over the each other still
maintaining own separate curls, proton smaller and electron bigger. % This one
% proton and one electron superpositioning is known as "Hydrogen-1 (protium)".

When curl and it's anticurl meet happens annihilation\cite{Annihilation} where
curl opens, gravity vanish and energy is again in electromagnetic form on
local space. Pair production\cite{PairProduction} can happen again from this
released energy.

\section{So called "weak interaction"}
\label{weak_interaction}
\index{weak interaction}

With the additional energy electron-curl $2426fm$\cite{ComptonWavelength}
can reach proton-curl size $1.321fm$ and form new harmonic curl called neutron
$1.319fm$. Due to needed extra energy neutron curl, even it's electric fields
sum outside seem to be zero, is affected by external electric disturbances and
cause neutron curl decay to proton and electron curl, average time to decay is
about fifteen minutes.

This decay is called to beta $\beta$-decay to and acting force is called to
weak force. Forces come during curl creation from electron Compton wavelength
shortening taken energy -- during size shrinking for electric field
strengthening done work, and proton positive, electron negative electric fields
mutual pulling force done work. These forces and work amounts are opposite
ones, partially cancel each other, causing sum force to look a like "weak
force" or "weak interaction". Interaction begin and end state energy levels we
can see from known rest masses whic directly relate to each separate or created
harmonic curl energy at rest.

\section{So called "strong interaction"}
\label{strong_interaction}
\index{strong interaction}

There is no strong interaction at all, seen strong interaction is relativistic
electromagnetic interaction. For example proton - proton interaction is two
different proton curls interaction, electromagnetic force pulls those away from
each other starting from long distances. While curls come near by each other
starting to form common harmonic curl, common relativistic space where both
electromagnetic waves fly at light speed, and outside observer sees static view
from curl having positive electric field towards outside observer. In this case
repelling forces are so big that formed harmonic curl "Helium-2 (diproton)"
isn't stable, and protons are immediately diverging apart.

If we combine above in weak interaction told proton and electron combination
called neutron with the proton we will get the stable "Hydrogen-2 (deuterium)"
harmonic curl having one positive electric field towards outside observer,
which easily form superposition with the additional electron curl.

Created harmonic curl has rest mass different from the incredients rest masses
and that is the needed or given energy during harmonic stable curl creation or
it's breaking, those are the strong forces at common harmonic curl -- atom core
creation and breakage.

We should not use human defined term time here at all because in the curl where
field stregth is so high that unlinearity exists and affects to electromagnetic
fields, forming space curling and related gravity. Electromagnetic forces
reactions in nuclear scale can be defined just by comparing the incredients and
results rest masses. Differencies are creating the dynamic forces driven
reactive movements on reaction.

Because peoples are so keen to use they time definition to understand reactions
we could give explanation using term time, so it might be helpful when reaching
the matter how strong nuclear force could be just electromagnetic force and
nothing else; When these separate waves are reaching near by, and they both are
on nearby light speed in they own curls, coming together enoug to form common
curl they propagate at light speed, which means that relativistic
electromagnetic force average affecting time, impulse time, shorter than what
static observer can see, ... and understand ;-), therefore observer sees "strong
interaction" because momentum is force multiplied with time, and now time is in
it's relativistic way 137\cite{FineStructureConst} times shorter electromagnetic
interaction than what observer thinks. This leads to situation where force has
to be 137 times stronger than static local observer thinks to get if same effect
happen in he's local reference frame. Users reference frame where curled space
internal time dilatation\cite{TimeDilation} is not seen.

And if change work get done, then later on uncurlig also give that same bang
backwards. Yep it's strong, but it's still electromagnetic force now forced to
happen to item going with light speed at start state in it's own curl.

This same process affects to all known more or less stable nuclides\cite{Nuclides}.
External conditions may wary, causing smaller or bigger probability for certain
combinations forming.

\begin{equation} \label{eq:clock_rate} % Lorentz factor
 \frac{1}{\gamma}=\sqrt{1-\frac{v^2}{c^2}}~~;~~\gamma=137.035999084
%137.035999177
\end{equation}

%\begin{equation} \label{eq:speed_rate}
%	\beta= \frac{v}{c}= \sqrt{1-\frac{1}{\gamma^2}}
%\end{equation}

%\begin{equation} \label{eq:speed_ratio}
%	\beta= \frac{v}{c}= \sqrt{1-\frac{1}{137^2}}= 0.99997
%\end{equation}

%\begin{equation}
%	\frac{v^2}{c^2}= 1-\frac{1}{\gamma^2}
%%	= n^{-2}
%\end{equation}

\begin{equation} \label{eq:speed}
	\frac{v}{c}=\sqrt{1-\frac{1}{\gamma^2}} ~=~ 0.99997
\end{equation}

%\begin{equation} \label{eq:reflective_ratio}
%	n^{-2}= \frac{\gamma^2-1}{\gamma^2}
%\end{equation}

%\begin{equation} \label{eq:reflective_ratio}
%%	n=
%	\frac{c}{v}=
%	\sqrt{\frac{\gamma^2}{\gamma^2-1}}=
%	1.000026627
%\end{equation}

%\begin{equation} \label{eq:refractive_index}
%	n= \frac{c}{v}= 1.000026627
%\end{equation}

Critical angle based to fine structure constant.

\begin{equation} \label{eq:critical_angle}
	\theta_c= \arcsin(\frac{v}{c}) = 1.5631~rad~89.556~deg
\end{equation}

%\begin{equation} \label{eq:critical_reflection_angle}
%	\theta_c= \arccos(\frac{v}{c}) = 0.0077~rad~0.4438~deg
%\end{equation}

By counting from speed difference how many internal reflections $Nr_{min}$
are needed to cover full circle $2\pi~rad = 360~deg$ we notice that about
406 reflections do the thing; Wave full internal reflection from minimum
matter amount, one electron itself.

\begin{equation} \label{eq:minimum_number_of_reflections}
	Nr_{min}\geq
	\frac {2\pi}{2\arccos(\frac{v}{c})}
	=\frac {\pi}{\arccos(\frac{v}{c})}
	= 405.58
\end{equation}

This gives kind of hint what we are looking for. Truth is some kind of limit
because formed electron or positron does not be full reflection instead it's
showing either negative or positive electric field outwards, but not both.
Kind of dot sized local space rotating so fast that light speed propagating
wave from external observers perspective seems to stay still without energy
loss or gain.

\section{Superpositioning}
\label{superpositioning}
\index{superpositioning}

Formed common curl -- atom core -- has positive electric field visible outside
and it attracts electron curls to superpositioned position balancing electric
fields. Superpositioned electrons are relatively loosely connected and related
to chemical properties of atom having core curl and superpositioned electrons.

Antimateria core curl have negative electric field visible outside and it
attracts positron curls to superpositioned position balancing electric fields
towards the outside local observer.

\section{Tunneling}
\label{tunneling}
\index{tunneling}

We do not live in isolation. Electromagnetic radiation in different waveforms,
curls, harmonic curls, superpositioned curls and exitation levels in any local
coordinate system having any speed level is still under radiation starting
from thermal radiation towards high energy cosmic rays.

Electromagnetic waves can be summed up to sum wave and this holds over the
space inluding the formed curls, harmonic curls and they exitation levels.
Therefore some curls forming the barrier and others being trapped in can sum
up with the external wave weakening barrier or strengthening the trapped curl
so that summed curl can pass the barrier curls formed barrier.

\section{Nuclear reactions}
\label{nuclear_reaction}
\index{nuclear reaction}

Radioactive decay is statistical value for the different curls, harmonic sum
curls aka nucleus lifetime in the local reference frame under background
radiation condition and referred material bulk own internal statistical state.

When there is external disturbance, background radiation and surrounding culrs
own curvature "gravity" and possible reaction pressure is affecting we see
different reactions, changes to harmonic sum curls listed in nuclides
chart\cite{Nuclides}, changes between the more or less stable harmonic
waveforms in referred background environment.

Certain bulk material combinations can introduce chain reactions where initial
curl breakage could introduce sub curls extraction and cause more curls to
break in chain reaction aka fission.

Gravity and reaction pressure can also introduce and maintain existing curls
merge or fusion to bigger harmonic curls in chain reaction way. Reactions can
be exotermic releasing radiation and kinetic energy or endotermic by storing
energy to created curl.

These defined reactions are reactions under one handed material bulks. Meaning
other handed antimaterial curls participance to reactions is neglible.

\section{Big Bang}
\label{big_bang}
\index{big bang}

Even material production is shown mostly be pair production creating 50\%
matter and another 50\% of antimatter. Due to matter and antimatter
annihilation process repeats several times before local cumulation occur.
Withing existing local cumulations, probability that matter can stay longer
intact grows. There will be places having more matter and other places having
more antimatter. This way material probability survive longer grows. Any
asymmetry in creation will boost cumulation significantly because there is no
need to have huge distances between before massive cumulations can occur
without risk to sudden annihilation due gravity merged local material and
antimaterial cumulations collision.

Due to expected amount of energy and mass of big bang incredients must had,
we could say that black holes are in some amount reversible or recursive.
Because you can't have that amount mass, localized energy, without black hole
formation before bang.

Most obvious explanation for the big bang is supermassive antimaterial and
material back holes collision and expansion in combined black hole or
expansion outside of combined black hole due the material annihilation in big
way, same time opening each particle curl which remove gravity and
electromagnetic radiation pressure overcome reduced gravity even pair
production try to maintain it, in these circumstances immediate annihilation
occur and radiation energy is free to enlarge space or even escape from black
hole in form of big bang.

Other explanation is that material and antimaterial black holes merged by
exploding blackhole internal structure we are part of. This leads to
fractalistic structure of space.

%Each kilogram corresponds to 25TWh of electricity.
%The whole human race yearly energy consumption equivalents 6400kg massloss.

\section{Dark Matter}
\label{dark_matter}
\index{dark matter}

Space might be fractalish having space and blackholes in blackholes, then
average density can be higher in inner space than what local observer can
notice in near by environment, or there are unknown, unnoticed curl forms
not affecting nor reacting with the known forms.

\section{Geat Void}
\label{great_void}
\index{great void}

One explanation to great void formation in to space is an gigantic antimaterial
mass passage through space, causing material annihilation. Interesting thing is
could this passage formation be dated somehow, and does it have any relation to
original big bang?

\section{Accelerator physics}
\label{accelerator_physics}
\index{accelerator physics}

High energy accelerator physics has filled gaps from Live Chart of Nuclides
\cite{Nuclides}, given lot of Feynmann diagrams\cite{FeynmannDiagram}.

\begin{comment}\end{comment}
%-END OF INCLUDE FILE----------------------------------------------------------
